What does the crowd believe?

### 2016-08-09 presentations/01_CogSci_2016/slides.Rmd
CogSci slides update; posterir P-value plots

## to do

- posterior predictive checks for individual-level $P_{ij}$

- posterior predictive <span style = "font-style: italic">p</span>-value with test statistics:
    - entropy of normalized slider ratings per subject
    - mean of normalized slider ratings per subject

>>>>

## posterior predictive p-values

<div align = 'center'>
  <img src="//Users/micha/Desktop/data/svn/priors/models/04_Exp2_Manski_JAGS/plots/posteriorPvalues_individualSliders.png" alt="posteriorP" style="width: 750px;"/>
</div>
